### 2018-02-27 Paper/jaccardbaetica.tex
update material and method

All the amphora stamps belong to Dressel 20 types. Dressel 20 was used to transport olive oil along the province during the Roman Empire. There is evidence that stamps were used from three centuries. (economía oleica betica). Frequently, stamps were marked mostly in handles but rarely in rims and body.  
The information of the stamps is known as \textit{tria nomina} (HABLAR SOBRE EL DEBATE DE LOS INDIVIDUOS DE ACEITE O YO QUE SE). \textit{Tria Nomina} was mostly formed for a code three of letters. These letters can appear in a abbreviated form or complete \citep{berni_millet_amphora_1996}

@@

A measure of dissimilarity has been chosen to analyse the dataset. We use the statistical technique Morisita-Horn index. This method was performed to measure the overlap between different samples of sets \citep{horn_measurement_1966}. In Ecology, it describes the dissimilarity between the system of two communities.

Considering our dataset as non-uniform sample, this method provides a useful tool to handle large samples with different sizes and diversity \citep{wolda_similarity_1981}. Morisita-Horn index can be expressed considering 0 as total presence of similarity of stamps and 1 a totally dissimilarity between stamps. In our case, it will be calculated the number of times that one stamp appear in a amphora workshop. This method allows to bear in mind the similar number of times for each repeated stamp per workshop.

>>>>

All the amphora stamps belong to Dressel 20 types. Dressel 20 was used to transport olive oil along the province during the Roman Empire. Most Dressel 20 were marked in stamps and tituli picti and inked in graffities with different information but there is not a general consensus about the meaning of them \citep{rodriguez_baetican_1998}. Stamps are the most studied in this type of amphorae. There is evidence that stamps were used from three centuries. (economía oleica betica). Frequently, stamps were marked mainly in handles but rarely in rims and body.

The information of the stamps is known as \textit{tria nomina} (HABLAR SOBRE EL DEBATE DE LOS INDIVIDUOS DE ACEITE O YO QUE SE). \textit{Tria Nomina} was mostly formed for a code three of letters. These letters can appear in a abbreviated form or complete \citep{berni_millet_amphora_1996}

@@

%quizás habría que hablar también del filtrado de códigos que se hizo en python porque antes había 3783 stamps pero se filtró por el número de letras...

The approach proposed here is based on the idea of measuring the similarity between amphora workshops by quantifying similar stamps. A measure of dissimilarity has been chosen to analyse the dataset. We use the statistical technique Morisita-Horn index. This method was performed to measure the overlap between different samples of sets \citep{morisita_measuring_1959, horn_measurement_1966}. In Ecology, it describes the dissimilarity between the system of two communities.

Considering our dataset as non-uniform sample, this method provides a useful tool to handle large samples with different sizes and diversity \citep{wolda_similarity_1981}. Morisita-Horn index can be expressed considering 0 as total presence of similarity of stamps and 1 a totally dissimilarity between stamps. In our case, it will be calculated the number of times that one stamp appear in a amphora workshop. This method allows to bear in mind the similar number of times for each repeated stamp per workshop. 
%quizas ampliar con el método de xavielin
